---
title: Portfolio Revisions"
author: "Zarina Yunis"
format: html
execute: 
  error: false
editor: visual
---

### Lab 4 Question 2

```{r}
{r}
#| warning: false

regions <- avocadoes |>
  filter(region %in% c("GreatLakes", "Northeast", "Plains", "SouthCentral", "Southeast", "West"))
regions_updated <- avocadoes |> 
  semi_join(regions, avocadoes, by = "region")
```

```{r}
#| warning: false
#| message: false

unwanted <- avocadoes |> 
  filter(region %in% c("California", "TotalUS"))
metro <- avocadoes |> 
  anti_join(regions_updated) |> 
  anti_join(unwanted) |> 
  rename("small.avocados" = `4046`,
         "large.avocados" = `4225`,
         "xl.avocados" = `4770`)
```

I included this question in my revisions because Lab 4 and the concepts associated with it were ones I particularly struggled with. I had completed revisions for Lab 4 earlier in the quarter, however I realized that there were still a number of concepts that I wasn't understanding when I received my second round of revisions. Taking a second or third look at this question and these concepts made me realize the difference between filtering rows in a dataframe by a certain characteristic and filtering items in a vector. I realized that the point of semi and anti-join was to create a new data set and then filter the original data set by this new data set, either by including the items in the new data set or by excluding them.
