---
title: "Challenge 9"
author: "Zarina Yunis"
format: 
  html:
    self-contained: true
execute: 
  error: true
  warning: false
  message: false
editor: visual
---

*This is an additional revision done for the portfolio*

```{r}
library(tidyverse)
library(knitr)
library(DT)
```

1.  ***revised question***

    -   **Added a datatable preview to the beginning of my document**

```{r}
#| echo: false
#| warning: false

a_names <- read_csv(here::here("supporting_artifacts", "StateNames_A.csv"))
datatable(head(a_names, n = 10), class = 'cell-border stripe')
```

```{r}
a_names <- a_names |> 
  rename("Sex" = "Gender")
```

## Summarizing and Visualizing the Numbers of Allisons

2.  

```{r}
summary_table <- a_names |> 
  filter(Name == "Allison") |> 
  group_by(State, Sex) |> 
  summarize(Count = sum(Count)) |> 
  pivot_wider(names_from = Sex, values_from = Count) |> 
  mutate(across(c("F", "M"), ~replace_na(., 0))) |> 
  filter(!"M" == 0)
kable(head(summary_table), 
      'html', 
      col.names = c("State", "F", "M"),
      align = "c",
      caption = "Distribution of Female and Male Allisons by State")
  
```

3.  

```{r}
female_allisons <- a_names |> 
  filter(Name == "Allison",
         Sex == "F") |> 
  group_by(Year) |> 
  summarize(Count = sum(Count))

```

4.  

```{r}
female_allisons |> 
  ggplot(mapping = aes(x = Year,
                       y = Count)) +
  geom_col(fill = "purple") +
  labs(y = "Number of Allisons")
```

## Modeling the Number of Allisons

5.  

```{r}
female_allisons |> 
  ggplot(mapping = aes(x = Year,
                       y = Count)) +
  geom_point(position = "jitter") +
  stat_smooth(method = "lm")
kable((female_allisons), 
      'html', 
      col.names = c("Year", "Count"),
      align = "c",
      caption = "Number of Allisons Born Per Year")
```

6.  

```{r}
allisons_lm <- female_allisons |> 
  lm(Count ~ Year, data = _)
allisons_lm
```

7.  

```{r}
allisons_lm |> 
  broom::augment() |> 
  ggplot(mapping = aes(y = .resid, x = .fitted)) +
  geom_point()
```

## Spelling by State

8.  

```{r}
allan <- a_names |> 
  filter(Name %in% c("Allan", "Alan", "Allen"))
kable(head(allan), 
      "html", 
      col.names = c("Name", "Year", "Sex", "State", "Count"),
      align = "c",
      caption = "Number of Allen/lan/llans Born Per Year Per State")
```

9.  

```{r}
allan |> 
  ggplot(mapping = aes(x = Year,
                       y = Count,
                       fill = Name)) +
  geom_col() +
  facet_wrap(~ Name)
```

10. 

```{r}
allan_ca_and_pa <- allan |> 
  filter(State %in% c("CA", "PA"), 
         Year == 2000,
         Sex == "M") |>  
  pivot_wider(names_from = Name,
              values_from = Count) |>
  select(State:Allan) |> 
  mutate(across(c("Alan":"Allan"), ~replace_na(., 0)))
kable(allan_ca_and_pa, 
      "html", 
      col.names = c("State", "Alan", "Allen", "Allan"),
      align = "c",
      caption = "Number of Allen/lan/llans Born Per Year Per State")
```

11. ***revised question***

    -   **Included an output of my percentages table for the amount of Allan/lan/llen's per state**
    -   **Played around with the different arguments to make my new data table neat, organized, and easy to follow**

```{r}
percentages <- allan_ca_and_pa |> 
  mutate(Total = rowSums(across(.cols = c("Alan", "Allen", "Allan"))),
         Alan = round((Alan / Total) * 100, 2),
         Allen = round((Allen / Total) * 100, 2),
         Allan = round((Allan / Total) * 100, 2)) |> 
  select(State:Allan)
datatable(percentages, 
          class = "cell-border stripe",
          editable = "cell",
          caption = "Percentages of 'Allen/an' per State")
```
